Fusion Moves for Correlation Clustering

### 2014-11-14 paper/evaluation.tex
typos found by paul

%!TEX root = ./egpaper_for_review.tex
\subsection{Evaluation}
For the evaluation of the different methods on the datasets introduced in Sec.~\ref{sec:datasets},
we show zoomed anytime plots in  Fig.~\ref{fig:anytime} and variation of information (VOI)~\cite{meila-2003}
and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
Anytime plots with no zooming and a detailed evaluation are given in supplementary material. 
%
For \emph{social-nets} CC-Fusion methods provide the best results for the first minutes .
Only CGC and HC-CGC are able to find better solutions after more than 1000 seconds.
MC-I and MC-R can not be applied to such large problems.
We belief that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generator would be a scalable implementation of the 
PIVOT algorithm.
%
For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even CC-Fusion 
and the used parameters have not been designed and chosen for this type of problem.
Especially it does a better job than MC-I.
%
For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
Because  the models are designed to have a high boundary recall (oversegmentation), 
classical fusion, which return undersegmentations, is best best VOI but worse RI and energy.
Proposals generated by EHC seemed to be a bit better than WS-based ones.
%
For the \emph{knott-datasets}
with increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.
The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
For the largest 3D volume seg-3d, HC-CGC gives the first useful solution, \cf  Fig.~\ref{fig:anytime}(f).
However, after a few minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
%
Pure EHC, Fusion and PIVOT-BOEM do not give useful results on any dataset.

>>>>

%!TEX root = ./egpaper_for_review.tex
\subsection{Evaluation}
For the evaluation of the different methods on the datasets introduced in Sec.~\ref{sec:datasets},
we show zoomed anytime plots in  Fig.~\ref{fig:anytime} and variation of information (VOI)~\cite{meila-2003}
and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
Anytime plots with no zooming and a detailed evaluation are given in the supplementary material. 
%
For \emph{social-nets} CC-Fusion methods provide the best results for the first minutes .
Only CGC and HC-CGC are able to find better solutions after more than 1000 seconds.
MC-I and MC-R can not be applied to such large problems.
We believe that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generator would be a scalable implementation of the 
PIVOT algorithm.
%
For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even though CC-Fusion 
and the used parameters have not been designed and chosen for this type of problem.
Especially it does a better job than MC-I.
%
For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
Because  the models are designed to have a high boundary recall (oversegmentation), 
classical fusion, which return undersegmentations, has best VOI but worse RI and energy.
Proposals generated by EHC seemed to be a bit better than WS-based ones.
%
For the \emph{knott-datasets}
CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance with increasing problem size compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.
The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
For the largest 3D volume seg-3d, HC-CGC gives the first useful solution, \cf  Fig.~\ref{fig:anytime}(f).
However, after a few minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and are also overall best in terms of energy, VOI, and RI.
%
Pure EHC, Fusion and PIVOT-BOEM do not give useful results on any dataset.

### 2014-11-14 paper/inputs/fig_fusion.tex
update 4.1 including figures
typos found by paul

    \end{tikzpicture}
}
\caption{
To fuse two edge labelings $y'$ and $y''$ with fusion moves
as defined by Lempitsky \etal~\cite{Lempitsky-2010} 
$y'$ and $y''$ need to be transfered to the node domain.
The mapping from edge labels to node labels is ambiguous and
even for this small graph there are seven node labels
which result in different binary fusion move problems.
Enumerating all labelings for a graph of non trival size
becomes intractable and choosing one labeling is complexity arbitrary.
%
%Furthermore it should be noted that 
}\label{fig:fusion_abiguty}
\end{figure}
\end{center}

>>>>

    \end{tikzpicture}
}
\caption{
To fuse two edge labelings $y'$ and $y''$ with fusion moves
as defined by Lempitsky \etal~\cite{Lempitsky-2010} 
$y'$ and $y''$ need to be transferred to the node domain.
The mapping from edge labels to node labels is ambiguous and
even for this small graph there are seven node labels
which result in different binary fusion move problems.
Enumerating all labelings for a graph of non trival size
becomes intractable.% and choosing one labeling is completely arbitrary.
%
%Furthermore it should be noted that 
}\label{fig:fusion_abiguty}
\end{figure}
\end{center}

### 2014-11-14 paper/introduction-new.tex
typos found by paul

Its value is, firstly, that it accommodates both positive (attractive) \emph{and} negative (repulsive) edge weights,
which allows doing justice to evidence in the data that two nodes or pixels do not wish or do wish to end up in the same cluster or segment, respectively.
Secondly, it does not require a specification of the number of clusters beforehand.

In signed social networks, where positive and negative edges encodes friend and foe relationships, respectively,
correlation clustering is a natural way to detect communities~\cite{Chierichetti-2014,Chen-2012}.
Correlation clustering can also been used to cluster query refinements in web search~\cite{Sadikov-2010}.
Because social and web-related networks are often huge, heuristic methods, \eg the PIVOT-algorithm~\cite{Ailon-2008},
are popular~\cite{Chierichetti-2014}.

@@

While it has a clear mathematical formulation and nice properties,
correlation clustering suffers on its NP-hardness. 
%
Consequently, partition problems on large scale data, \eg
huge volume images in computational neuroscience~\cite{kroeger_2012_eccv}
or social networks~\cite{Leskovec-2010}, 
are not tractable because reasonable solutions cannot be computed in acceptable time.

@@

\vspace{0.1cm}
\noindent \textbf{Related Work.}
A natural approach is to solve the integer linear program (ILP) directly. 
To this end, efficient separation procedures have been found~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
Alternatively, it is possible to relax the integrality constraints of the ILP formulation~\cite{kappes_2013_arxiv}. 
Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
For the latter approach column generating methods exits, which work best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.

Another line of work uses move making algorithms 
to optimize correlation clustering~\cite{bagon_2011_arxiv,beier_2014_cvpr,Kernighan-1970}.
Starting with an initial segmentation, auxiliary max-cut problems are (approximately) solved,
such that the segmentation is strictly improved.
As shown in~\cite{beier_2014_cvpr} only Cut, Glue \& Cut (CGC)
can deal with large scale problems, but can also suffer on very large auxiliary problems.

Outside computer vision greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} have been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
The PIVOT Algorithm~\cite{Ailon-2008} iterates over all nodes in random order.
If the node is not assigned it constructs a cluster containing the node and all its 
unassigned positively linked neighbors.  
%
A widely used post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigns nodes to clusters.

For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art any time performance~\cite{kappes_2014_ws}.
Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} cannot be applied directly for correlation clustering.
We will show how to overcome this point in Sec.~\ref{sec:cc_fm}.

\vspace{0.1cm}
\noindent \textbf{Outline:} 
In Sec.~\ref{sec:problem_formulation} we will give a 
detailed problem definition and introduce 
the correlation clustering objective.
Next we give a description of energy based hierarchical clustering in Sec.~\ref{sec:ehc} and
our proposed correlation clustering fusion moves in Sec.~\ref{sec:cc_fm}.
We evaluate the proposed methods methods in Sec.~\ref{sec:exp} and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.

>>>>

Its merit is, firstly, that it accommodates both positive (attractive) \emph{and} negative (repulsive) edge weights,
which allows doing justice to evidence in the data that two nodes or pixels do not wish or do wish to end up in the same cluster or segment, respectively.
Secondly, it does not require a specification of the number of clusters beforehand.

In signed social networks, where positive and negative edges encode friend and foe relationships, respectively,
correlation clustering is a natural way to detect communities~\cite{Chierichetti-2014,Chen-2012}.
Correlation clustering can also be used to cluster query refinements in web search~\cite{Sadikov-2010}.
Because social and web-related networks are often huge, heuristic methods, \eg the PIVOT-algorithm~\cite{Ailon-2008},
are popular~\cite{Chierichetti-2014}.

@@

While it has a clear mathematical formulation and nice properties,
correlation clustering suffers from NP-hardness. 
%
Consequently, partition problems on large scale data, \eg
huge volume images in computational neuroscience~\cite{kroeger_2012_eccv}
or social networks~\cite{Leskovec-2010}, 
are not tractable because reasonable solutions cannot be computed in acceptable time.

@@

\vspace{0.1cm}
\noindent \textbf{Related Work.}
A natural approach is to solve the integer linear program (ILP) directly. 
To this end, efficient separation procedures have been found~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
Alternatively, it is possible to relax the integrality constraints of the ILP formulation~\cite{kappes_2013_arxiv}. 
Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and therefore rounding is required to obtain a valid partitioning.
For the latter approach column generating methods exist, which work best on planar \cite{yarkony_2012_eccv} graphs. %or almost planar \cite{yarkony-andres-2013} graphs.

Another line of work uses move making algorithms 
to optimize correlation clustering~\cite{bagon_2011_arxiv,beier_2014_cvpr,Kernighan-1970}.
Starting with an initial segmentation, auxiliary max-cut problems are (approximately) solved,
such that the segmentation is strictly improved.
As shown in~\cite{beier_2014_cvpr} only Cut, Glue \& Cut (CGC)
can deal with large scale problems, but can also suffer from very large auxiliary problems.

Outside computer vision, greedy methods~\cite{Soon-2001,Ng-2002,Gionis-2007,Elsner-2008,Ailon-2008} have been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
The PIVOT Algorithm~\cite{Ailon-2008} iterates over all nodes in random order.
If the node is not assigned it constructs a cluster containing the node and all its 
unassigned positively linked neighbors.  
%
A widely used post-processing method is  Best One Element Move (BOEM)~\cite{Gionis-2007}, which iteratively reassigns nodes to clusters.

For energy minimization problems fusion moves have become increasingly popular~\cite{Lempitsky-2010,kappes_2014_ws}.
For many large scale computer vision applications fusion moves lead to good approximations
with state of the art anytime performance~\cite{kappes_2014_ws}.
Due to the ambiguity of a node-labeling, classical fusion moves~\cite{Lempitsky-2010} cannot be applied directly for correlation clustering.
We will show how to overcome this problem in Sec.~\ref{sec:cc_fm}.

\vspace{0.1cm}
\noindent \textbf{Outline:} 
In Sec.~\ref{sec:problem_formulation} we will give a 
detailed problem definition and introduce 
the correlation clustering objective.
Next we give a description of energy based hierarchical clustering in Sec.~\ref{sec:ehc} and
our proposed correlation clustering fusion moves in Sec.~\ref{sec:cc_fm}.
We evaluate the proposed methods in Sec.~\ref{sec:exp} and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.
